Concurrent Programming with CXL

### 2020-06-26 book/paper.tex
Better variable name

Using a lock is a good thought, but how does one implement one?
Figure~\ref{fig:uplock} presents a mutual exclusion attempt based on a
na\"{\i}ve (and, as it turns out, broken) implementation of a lock.
Initially the lock is not owned, indicated by lock being \texttt{False}.
To enter the critical section, a process waits until \textit{lock} is \texttt{False}
and then sets it to \texttt{True} to indicate that the lock has been taken.
The process then executes the critical section.  Finally the process
releases the lock by setting it back to \texttt{False}.

Unfortunately, if we run the program through CXL, we find that the assertion still
fails.  Diagnosing the problem, we see that the \textit{lock} variable
suffers from the same problem as the \textit{count} variable
in Figure~\ref{fig:inc}: operations
on it consist of several instructions.  It is thus possible
for both processes to believe the lock is available and to obtain the lock
at the same time.

>>>>

Using a lock is a good thought, but how does one implement one?
Figure~\ref{fig:uplock} presents a mutual exclusion attempt based on a
na\"{\i}ve (and, as it turns out, broken) implementation of a lock.
Initially the lock is not owned, indicated by \textit{lockTaken} being \texttt{False}.
To enter the critical section, a process waits until \textit{lockTaken} is \texttt{False}
and then sets it to \texttt{True} to indicate that the lock has been taken.
The process then executes the critical section.  Finally the process
releases the lock by setting \textit{lockTaken} back to \texttt{False}.

Unfortunately, if we run the program through CXL, we find that the assertion still
fails.  Diagnosing the problem, we see that the \textit{lockTaken} variable
suffers from the same problem as the \textit{count} variable
in Figure~\ref{fig:inc}: operations
on it consist of several instructions.  It is thus possible
for both processes to believe the lock is available and to obtain the lock
at the same time.
